---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# generations


The goal of generations is to allow users to calculate the number of “generations” since the first value in a variable. It is imagined for use with years, but can be used with any dbl variable. As we study generational effects in sociology, genetics and genomics, and more, a quick method of calculating generations like this is necessary. 

## Installation

Since this package is not yet published on CRAN, use `devtools::` to load it. 
```{r}
#devtools::install_github("ewincm15/generations")
```

## Example

This is a basic example which shows you how to solve a common problem, using the default `generationtime` of 25 years (so called because of human generation times):

```{r example}
library(generations)
gen(c(1559, 1996, 1448, 1668, 1773))
```

Here is an example of changing the default generation time to 3 years, to calculate the generations for meerkats, for example: 

```{r example2}
gen(c(2005, 1778, 2012, 1987, 1654, 1328), generationtime = 3)
```

## Building `generations`

Here are the packages and functions I used to prepare the package:
```{r}
#library(devtools)
#create_package()
#use_git()
#use_r("generations")
#library(testthat)

```

Here is the function contained in the package: 
```{r}
#gen <- function(data, na.rm = TRUE, verbose = TRUE, generationtime = 25){
  #if(verbose) message("Calculating number of generations")
  #data = sort(data)
  #test = (data - data[1])/generationtime
  #return (ceiling(test)  )
#}

```
I did not do any manual work with my files. 

## 'generations' in Context

`generations` currently only contains the function `gen`, which calculates generations. Any other imagining of how to calculate generations or how to display them is forthcoming. 

`generations` currently only takes numeric vectors. Accordingly, if data is in date formats, transforming it into dbl using the `lubridate::` package is recommended.

All objects (namely, `gen`) are exported and can be accessed via `generation::`.
